Beef Pricing Dynamics in the Canadian Grocery Market, 2024: A Comparative Analysis of Walmart and T&T

### 2024-11-29 paper/paper.qmd
final draft

---
title: "Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T"
subtitle: "Evidence of Cultural and Strategic Influences on Beef Pricing"
author: 
  - Ziheng Zhong
thanks: "Code and data supporting this analysis is available at: [Link to repository](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "This study examines beef pricing in the Canadian grocery market, focusing on Walmart and T&T as representative vendors. Using Bayesian linear regression, it analyzes how historical prices, vendor-specific strategies, and seasonal effects impact current beef prices. The findings indicate that historical pricing strongly predicts current prices, while vendor approaches differ significantly, with Walmart maintaining consistent pricing and T&T showing greater variability. This research highlights how cultural preferences and retail strategies influence food pricing, enhancing our understanding of market behavior and supporting both consumer choices and policy development."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-current_price
#| fig-cap: "Boxplot of the distribution of current prices"
#| echo: false
#| warning: false
#| message: false
#| fig-width: 5

>>>>

---
title: "Beef Pricing Dynamics in the Canadian Grocery Market, 2024: A Comparative Analysis of Walmart and T&T"
subtitle: "Evidence of Cultural and Strategic Influences on Beef Pricing"
author: 
  - Ziheng Zhong
thanks: "Code and data supporting this analysis is available at: [Link to repository](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "This study examines beef pricing in the Canadian grocery market, focusing on Walmart and T&T as representative vendors. Using Bayesian linear regression, it analyzes how historical prices, vendor-specific strategies, and seasonal effects impact current beef prices. The findings indicate that historical pricing strongly predicts current prices, while vendor approaches differ significantly, with Walmart maintaining consistent pricing and T&T showing greater variability. This research highlights how cultural preferences and retail strategies influence food pricing, enhancing our understanding of market behavior and supporting both consumer choices and policy development."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-current_price
#| fig-cap: "Distribution of current prices"
#| echo: false
#| warning: false
#| message: false
#| fig-width: 3
